Maps

### 2020-05-01 ms_8.Rmd
Giant sf object under construction

dsn1870 <- "raw-data/nhgis0002_shape/nhgis0002_shapefile_tl2008_us_county_1870"
  layer1870 <- "US_county_1870_conflated"
dsn1880 <- "raw-data/nhgis0002_shape/nhgis0002_shapefile_tl2008_us_county_1880"
  layer1880 <- "US_county_1880_conflated"
dsn1890 <- "raw-data/nhgis0002_shape/nhgis0002_shapefile_tl2008_us_county_1890"
  layer1890 <- "US_county_1890_conflated"
dsn1900 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1900"
  layer1900 <- "US_county_1900_conflated"
dsn1910 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1910"
  layer1910 <- "US_county_1910_conflated"
dsn1920 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1920"
  layer1920 <- "US_county_1920_conflated"
dsn1930 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1930"
  layer1930 <- "US_county_1930_conflated"
dsn1940 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1940"
  layer1940 <- "US_county_1940_conflated"
dsn1950 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1950"
  layer1950 <- "US_county_1950_conflated"
dsn1960 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1960"
  layer1960 <- "US_county_1960_conflated"

@@

# gis template for any year/variable desired
# only change these two lines!
year <- 1950

@@

>>>>

# I had to shorten the file paths in order to deploy my app
# The maps can no longer render in this directory as a result
dsn1870 <- "raw-data/nhgis0002_shape/nhgis0002_shapefile_tl2008_us_county_1870"
  layer1870 <- "US_county_1870_conflated"
dsn1880 <- "raw-data/nhgis0002_shape/nhgis0002_shapefile_tl2008_us_county_1880"
  layer1880 <- "US_county_1880_conflated"
dsn1890 <- "raw-data/nhgis0002_shape/nhgis0002_shapefile_tl2008_us_county_1890"
layer1890 <- "US_county_1890_conflated"

dsn1900 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1900"
  layer1900 <- "US_county_1900_conflated"
dsn1910 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1910"
  layer1910 <- "US_county_1910_conflated"
dsn1920 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1920"
  layer1920 <- "US_county_1920_conflated"
dsn1930 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1930"
  layer1930 <- "US_county_1930_conflated"
dsn1940 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1940"
  layer1940 <- "US_county_1940_conflated"
dsn1950 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1950"
  layer1950 <- "US_county_1950_conflated"
dsn1960 <- "raw-data/nhgis0003_shape/nhgis0003_shapefile_tl2008_us_county_1960"
  layer1960 <- "US_county_1960_conflated"

@@

# gis template for any year/variable desired
# only change these two lines!
year <- 1870

@@

# New Dataset for Mapping

```{r mwData-shapefile-merger}
# NEW tibble
# columns: COUNTYA?, YEAR, variable, value

mapData1 <- mwData %>% pivot_longer(cols = "Value of Farms":"Illiteracy Rate", names_to = "Variable")

mapData <- left_join(mapData1, shapefiles, by = c("YEAR" = "Year"))

```{r}
year <- 1870

datayear <- mapData %>%
  # use get() to use the stored variable
  # idk why, but it doesn't work without this
  # the variable must be converted to a double in the original mwData dataset
  filter(YEAR == year, Variable == myvar) %>%
  select(GISJOIN, YEAR, Variable, value, Dsn, Layer)

countyyear <- sf::st_read(dsn = dsnyear,
                         layer = layeryear)
# IN PROGRESS, START HERE
# make a huge sf object that has all of the info
# save as RDS
# use only one filter (for year and variable) with the code calling the palette and below

# wow you can save sf objects as RDS files, apparently!
# do this once you have everything done
# but then again, if I can save this as an RDS, do I actually need to pivot longer? does that make sense?
#saveRDS(countyyear, file = "testSfObj.rds")

leaflet(countyyear) %>%
  addTiles() %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.3, fillOpacity = 1,
              fillColor = ~pal(value)) %>%
  addLegend(pal = pal, values = ~value, opacity = 1.0, title = myvar)
```
